Cultural Evolution of Conservation Behavior at the Intersection of Working

### 2020-11-24 DissertationProposal/DissertationProposal.Rmd
Totally redid abm descriotion

--- 
title: Cultural Evolution of Conservation Behavior at the Intersection of Working
  Landscapes and Protected Areas
author: "Matt Clark"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: yes
  pdf_document:
    toc: yes
    extra_dependencies: "subfig"
  bookdown::html_document2:
    toc: yes
fontsize: 12pt
link-citations: yes
csl: AmJBot.csl
subtitle: Dissertation Proposal for Committee Review
bibliography: [References/Dissertationproposal.bib,References/NonZoteroRefs.bib]
---
```{r packages, include=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
library(formattable)
library(kableExtra)
library(dplyr)
library(magrittr)
library(prettydoc)
library(htmltools)
library(knitcitations)
library(devtools)
library(tidyverse)
library(scales)
library(extrafont)

@@

*Single group setup and basic function*

In the most simple scenario, the agent-based model represents a simplistic world where there is one homogeneous group of agents who harvest resources from a landscape. This landscape is divided into two types, working and protected. Resources move between these types at each time step with some probability. During initialization, the protected and working landscapes are both at an equal, designated percent carrying capacity. At each time step, agents aim to maximize their harvest up until a designated harvest max. During initialization, agents are assigned as either obligatory cooperators or as having the ability to defect to a small degree, spending a small portion of their time harvesting from the protected landscape.

The model also allows for ecological variation during the initial specification. The variable ecological starting conditions are as follows: Resource mobility designates the probability that a resource unit will move from the protected landscape into the working landscape or vice versa at each time step. Protected area size demarcates what percentage of the available resource units are within the protected area. Percent carrying capacity sets the total number of harvestable resource units as a percent of the landscape carrying capacity. Lastly, the resource regeneration rate designates what percentage the resource regenerates at each time step (see Table \@ref(tab:tabAbmVars)).

```{r tabAbmVars, echo=F, fig.align='center'}
abmVars <- data.frame(Parameters = c("Individuals","Total Carrying Capacity", "Percent Carrying Capacity", 
                                     "Percent Protected", "Starting Cooperators", "Time Steps", "Max Harvest",
                                     "Resource Regeneration",  "Resource Mobility","Groups","Learning Strategy", 
                                     "Percent Cooperation", "Average Payoff", "Protected Area Degredation",
                                     "Working Landscape Degredation"), 
                      Type = c("Starting Condition","Starting Condition","Starting Condition",
                               "Starting Condition","Starting Condition","Starting Condition",
                               "Starting Condition","Key Independent Variable","Key Independent Variable",
                               "Key Independent Variable","Key Independent Variable",
                               "Outcome","Outcome","Outcome","Outcome"), 
                      Description = linebreak(c("Number of agents in simulation",
                                      "Maximum number of resources\nallowed on landscape",
                                      "Percent of carrying capacity at\ninitialization",
                                      "Percent of landscape in\nprotected area",
                                      "Starting percent of agents\nfully cooperating",
                                      "Number of time steps\nsimulation will run for",
                                      "Maximum number of resources\nagents will harvest during\none time step",
                                      "The percent of available resources\nwhich will regenerate at each time\nstep in both protected and\nworking landscapes",
                                      "The probability that any available\nresource will move from the\n protected to working landscape\nor vice versa",
                                      "Solitary or multiple\ncompeting groups",
                                      "Assigns a percent of the population\nto success-biased imitation and\nthe remaining population to\nconformist-biased imitation",
                                      "Percent of total population\nharvest time spent in\nthe working landscape","Mean harvest for all agents\nat each time step",
                                      "Working landscape percent of\ntotal carrying capacity",
                                      "Protected area percent of\ntotal carrying capacity")))
knitr::kable(abmVars, caption = "Description of all model parameters.",escape=F) %>% 
  kable_styling(c("striped",full_width=F))%>% row_spec(0,bold=TRUE)

@@

The environment also responds to agent behavior. At every time step, both the protected and working landscapes lose exactly the number of resources that agents harvest from them. The areas then regenerate resources according to the regeneration rate per time step and lastly, the resources move from one area to the other with the probability specified during model initialization.

Agents behave according to a specific set of rules. Agents choose to spend a given percent of their time harvesting from the protected area (defecting) and a percent of their time harvesting from the working landscape (cooperating). Full defection is when the average percent of time agents spend in the protected area is equal to the percent of the landscape protected (i.e. they do not treat the protected area any differently than the working landscape).

Agents learn their behaviors according to one of two possible learning mechanisms. Agents who learn via success-biased learning will preferentially copy the behavior of more successful agents when they encounter them. Agents who learn via conformist-biased learning will disproportionately copy the behavior of other agents they see as being in the majority, regardless of the success of those agents. The learning strategy of the overall population will be an adjustable scale which assigns either a conformist-biased or success-biased learning strategy to a percentage of the agents. Behaviors may be modified at each time step by the key processes described below.

*Key processes*

For the given number of timesteps, the model follows a set of key processes. At time step one, all agents first spend their initial assigned percentage of effort harvesting from the working landscape. If agents reach the max harvest amount, they do not harvest from the protected landscape, even if they are assigned as having the ability to defect. If they do not reach harvest max, they will spend the rest of their effort harvesting from the protected area. They will harvest up to the harvest max if possible. The resulting resources in both landscapes are multiplied by the regeneration factor, not past the carrying capacity of the landscape. Resources move between the protected and working landscapes with a probability proportional to designated probability of mobility (see Table \@ref(tab:tabAbmVars)). If agents are following a success biased learning strategy, they are paired with another agent at random and compare strategies. If one agent performs worse than another in the first time step, the underperforming agent will adopt a strategy in-between (split the time difference in half) their previous strategy and the strategy of the agent who outperformed them. If agents are following a conformist strategy, they are grouped with 5 other agents at random at each time step, and adopt the mean strategy of all agents in their group. This process repeats for all time steps. This process is summarized conceptually in Fig \@ref(fig:conceptDiagram).

```{r conceptDiagram, echo=FALSE, fig.cap="Concept diagram of agent-based model scheduling under single group dynamics", out.width = "50%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ConceptDiagram.png")
```
*Multiple competing groups*

In the multiple competing groups scenario, two groups with separate resource pools will each follow the processes described above. However, at the end of each time step the groups will compare the average harvest rates. We assume that the underperforming group can observe the average harvest strategy (time spent in the protected or working areas) of the better performing group. A specified percent of the agents from the less successful group will subsequently adopt the average harvest strategy of the more successful group (see Table \@ref(tab:tabAbmVars)).

*Outcomes*

In both single and multiple group scenarios, the dependent variables of interest are as follows: Cooperative behavior reports the average time that agents spend harvesting from the working landscape in each time step. Full defection is defined as all agents harvesting from the protected landscape for a proportion of time equal to the percent of the resource which is protected. Protected area degradation measures the percent carrying capacity of the protected landscape. Working landscape degradation measures the percent carrying capacity of the working landscape. Lastly, mean payoff to individuals measures the average payoff that agents receive at each time step.

@@

## Preliminary Work
I have developed a model which follows the above processes for one group with one resource pool. An interactive application which performs one run of that model can be found here [(click!)](https://mattclarknewaccount.shinyapps.io/ABM_Output_trial/).

This model currently assigns one learning strategy to all agents in the population. Users can select either successes-biased or conformity-biased learning to be applied. Future development will allow users to specify the percent of the population employing each learning strategy as specified in the methods above.

Environmental conditions can be set to provide neither an over abundance of resources nor a restrictive scarcity. Under these conditions, we see conformity-biases maintain starting group norms around harvest behaviors. Of greater interest is that under success-biased learning, we observe that protected areas enhance agent wellbeing (average harvest) initially, but defection eventually spreads and causes a failure of the protected area as seen in Fig \@ref(fig:abmOutput). With this in-mind, the next step for this research is to introduce a second group dynamic which will allow us to test the logic of cultural group selection for costly conservation behaviors under these conditions.

```{r abmOutput, echo=FALSE, fig.cap="Fifteen example runs of the current, single group agent-based model. CC indicates the carrying capacity of the protected and working landscapes respectively. This model has been specified to neither provide an over abundance or scarcity of resources. Agents all learn via a success-biased strategy.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ABM_Output2.png")
```

## Expected Products
I plan to communicate the findings of this project both to the academic community and to non-scientists. The insights gained from this model will be published in a peer reviewed, academic journal such as Environmental Modeling and Software. This paper will show logically how we expect that protected areas function in the context of community level cooperative conservation. An example of how this model may inform implementation of protected areas for various resource mobilities or starting resource degradation is displayed in figures \@ref(fig:abmSim1) & \@ref(fig:abmSim2).

@@

```{r abmSim1, echo=FALSE, fig.cap="Simulated agent-based model output of conservation adoption under single group dynamics.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmSim1.png")
```

```{r abmSim2, echo=FALSE, fig.cap="Simulated agent-based model output of conservation adoption under multiple group dynamics.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmSim2.png")
```
\newpage

@@

In summary, conserving forest cover is critical for the global carbon balance and for the well-being of many rural communities. Conservation projects often fail due to a lack of consideration of the social processes underlying adoption. With few studies that measure transmission fidelity in a naturalistic setting, where outcomes have real economic and health impacts - we have an opportunity to explore how environmental constraints and social learning interact when outcomes matter. This project seeks to further investigate how and why behaviors are modified during the transmission process and how modification (both enrounious and intentional) affect performance targets.

@@

```{r mapp, echo=FALSE, fig.cap="Satellite map of Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "75%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/MapLines.png")
```

>>>>

--- 
title: Cultural Evolution of Conservation Behavior at the Intersection of Working
  Landscapes and Protected Areas
author: "Matt Clark"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: yes
  pdf_document:
    toc: yes
    extra_dependencies: "subfig"
  bookdown::html_document2:
    toc: yes
fontsize: 12pt
link-citations: yes
csl: AmJBot.csl
subtitle: Dissertation Proposal for Committee Review
bibliography: [References/Dissertationproposal.bib,References/NonZoteroRefs.bib]
---
```{r packages, include=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmarkdown)
library(bookdown)
library(formattable)
library(kableExtra)
library(dplyr)
library(magrittr)
library(prettydoc)
library(htmltools)
library(knitcitations)
library(devtools)
library(tidyverse)
library(scales)
library(extrafont)
```

@@

*Current Single Group Model - The Most Simple Case(s)*

In the most basic form, the current agent-based model demonstrates repeated subtractions from a multiplicatively regenerating quantity of resources. In this context, there are no resource protections and therefore agents cannot modify their harvest strategies. We can write a simple analytical model to better denote these dynamics and determine interesting and appropriate starting conditions for more complex permutations of the agent-based model, as well as validate our intuitions as to how the model should behave. 
Given that the resources regenerate multiplicatively, any starting conditions which cause the resource pool to diminish after the first time step will further deplete the ever-shrinking resource pool with each additional time step. Specifically, any max harvest value which when multiplied by the number of agents is greater than the number of resources that regenerate in the first time step, will cause the resource pool to continually diminish over time and eventually reach zero. We can define the sustainable harvest threshold (${H_{sust}}$) for any given number of agents (${N}$), starting resources (${W_{r}}$), and regeneration rate (${R}$) as:

$$H_{sust} \leq \frac{(1-R)*(W_{r}-H_{max}*N)}{N} $$

Figure \@ref(fig:FirstABM) shows the model behavior when the maximum harvest value is at the calculated sustainable harvest value for this scenario. We can see that the amount of resources harvested in each time step is below the amount regenerated, therefore we see no change in the available and harvested resources over time.

```{r FirstABM, out.width = "100%",echo=FALSE, fig.align='center', dpi=72, fig.pos= "H",fig.cap="Resource quantity and mean harvest values over time for one run of the agent-based model at a maximum harvest value exactly at the calculated value for sustainable harvest. Model starting conditions include 100 individuals harvesting from a landscape of 10000 resources. The regeneration factor at each time step is 1.20."}
knitr::include_graphics("Figures/Ch1/abmP1a.png")
```

In contrast to the figure above, figure \@ref(fig:FirstABMb) shows the model behavior when the maximum harvest value is just one over the calculated sustainable harvest value. In this scenario, we can see that the resource pool becomes more depleted over time and the quantity of resources regenerated at each time step is reduced proportionally.

```{r FirstABMb, out.width = "100%",echo=FALSE, fig.cap="Resource quantity and mean harvest vales over time for one run of the agent-based model at a maximum harvest valuue one above the calculated value for sustainable harvest. Model starting conditions include 100 individuals harvesting from a landscape of 10000 resources. The regeneration factor at each time step is 1.20.", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmP1.png")
```

We can extend this model to explore how the sink/source dynamics between protected areas and adjacent working landscapes may provision more renewable resources than working landscapes alone. In this formation, we still have one homogenous group of agents who harvest regenerating resources from a landscape. This landscape now has some specified percentage sectioned off and inaccessible to the agents — the protected area. At every time step agents will attempt to harvest resources from the working landscape up until the specified maximum harvest amount. The outcome of this harvest attempt for each agent is the result of one random draw from a Binomial distribution where the number of trials is equal to the number of resources available on the working landscape divided by the number of individuals (i.e. that individual’s share of the available resources) and the probability of success is equal to the percent of an agent’s harvest time spent in the working landscape; in this scenario we are forcing obligatory cooperation so that percentage is always 100%. This will not always be the case as we build complexity in the model.

After the agents harvest resources from the landscape, the resources in the working and protected areas will reproduce by the specified regeneration factor. If the number of resources in either area exceeds the allotted carrying capacity, the excess resources will either die (i.e. not be available for agents in the following time step) or move to the other area (protected or working) with some specified probability also applied to a Binomial distribution. Resources which move to the adjacent area but exceed the carrying capacity will also die. If we set the probability of resource mobility to 100%, we can now calculate the maximum sustainable harvest amount for each agent where the only modification to the equation is the addition of mobile resources from the protected area (${P_{mob}}$) up until a specified carrying capacity ($W_{cc}$).

$$P_{mob} = (R*P_{r})-P_{r}$$

$$H_{sust} \leq \frac{(1-R)*(W_{r}-H_{max}*N)+min\{P_{mob},W_{cc}-W_{r}\}}{N} $$

Note that the sustainable harvest value is now dependent on the percent of the resources in the working landscape vs the protected area. We can run the model for every combination of protected area sizes and maximum harvest values to make sure that the model outcomes match out analytical intuition (fig \@ref(fig:abm2)). In the figure below, we can see that up until the maximum sustainable harvest value for this scenario (16), agents will always reach the set maximum harvest value until the resources are no longer made available to them (i.e. all protected). Above the maximum sustainable harvest value, the size of the protected area becomes greatly important for determining average harvest payoff to agents. In this scenario where the resources regenerate at a relatively high rate (20%) and the probability of mobility is 100%, the sink/source dynamics allow agents to reach the greatest average harvest value when the protected area is large and therefore provisioning many resources to the ever depleting working landscape at every time step.

```{r abm2, out.width = "75%",echo=FALSE, fig.cap="Average harvest values for all agents in the final time step (30) for many combinationa of maximum harvest values and protected area sizes. Model starting conditions include 100 individuals harvesting from a landscape of 10000 resources. The regeneration factor at each time step is 1.20.", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmp2.png")
```

*Current Single Group Model - Incorporating Uncertainty*

Up to this point, we have assumed that excess resources produced in the protected area will move to the working landscape, up until a specified carrying capacity, with 100% probability. Key insights from this model are gained from experimenting with different probabilities of resource mobility. To frame this in the context of real world protected areas, we can assume that insights from model runs with high probabilities of resource mobility may be applied to wide ranging organisms such as large aquatic animals, while model runs with low probabilities of resource mobility may be applied to relatively low vagility organisms such short or large-seeded trees [@thomson2011seed].

The probability of resource mobility is operationalized in the model by using random draws from a Binomial distribution. For every resource unit regenerated over the carrying capacity of the protected area, we take one random binomial draw with the probability of success equal to the probability of resource mobility. With all other model specifications kept equal and a maximum harvest value set slightly above the maximum sustainable harvest value for a working landscape alone, we can explore the interaction between protected area size and resource mobility given obligatory cooperation.

```{r abm3, out.width = "75%",echo=FALSE, fig.cap="Average harvest values for all agents in the final time step (30) across five runs of the model. Outcomes are the result of many combinations of resource mobilities and protected area sizes. Model starting conditions include 100 individuals harvesting from a landscape of 10000 resources. The regeneration factor at each time step is 1.20 and the maximum harvest value is set to 25.", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmp3.png")
```

*Current Single Group Model - Cooperation, Defection, & Social Learning*

To apply this model to conservation adoption and different mechanisms of social learning, we can allow agents to alter their harvest strategies beyond obligatory cooperation around protected area regulations. During model initialization, we can set the percentage of agents who we will allow to spend a proportion of their harvest effort in the protected area (defecting). The proportion of effort an individual agent spends in the protected area is drawn from the beta distribution below (fig \@ref(fig:betastart)) to ensure that the majority of effort is still spent in the working landscape at initialization.

```{r betastart, out.width = "75%",echo=FALSE, fig.align='center', fig.pos= "H", fig.cap="One thousand random draws from a beta distribution with the shape 1 and 2 parameters set at 1 and 2 respectively. This distribution is used to assign the harvest effort spent in the protected area for defecting agents during model initialization."}
hist(rbeta(1000,1,2),main=NULL)
```

At each time step, all agents first harvest resources from the working landscape. The number of resources agents receive from the working landscape is determined by one draw from the binomial distribution where the number of trials is equal to the number of resources in the working landscape divided by the number of agents and the probability of success is equal to the percentage of effort that agent spends in the working landscape. Agents only harvest resources up to the specified maximum harvest value.

After harvesting from the working landscape, agents who defect to some degree and did not already reach the maximum harvest value, spend the remainder of their harvest effort in the protected area. Following the same logic as harvest from the working landscape, the number of resources agents receive from the protected area is determined by one draw from the binomial distribution where the number of trials is equal to the number of resources in the protected area divided by the number of agents who defect in that time step and the probability of success is equal to the percentage of effort that agent spends in the protected area.

Agents modify their behavior (the percentage of time they spend in each area) at each time step according to one of two learning strategies. If agents are following a success-biased learning strategy, they are paired with another agent at random at each time step and compare strategies. If one agent performs worse than another in the previous time step, the underperforming agent will adopt a strategy in-between (split the time difference in half) their previous strategy and the strategy of the agent who outperformed them. If agents are following a conformist-biased strategy, they are grouped with 5 other agents at random at each time step, and adopt the mean strategy of all agents in their group. The learning strategy of the overall population is currently set to either success-biased or conformist-biased learning for all agents, but in future versions of the model, it will be an adjustable scale which assigns either a conformist-biased or success-biased learning strategy to a percentage of the agents. The entire model process is visualized conceptually in the figure below and a table of all the model starting conditions, key variables, and outcomes can be found in Table \@ref(tab:tabAbmVars)).

```{r conceptDiagram, echo=FALSE, fig.cap="Concept diagram of agent-based model scheduling under single group dynamics", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ABMConceptDiagramFinal.png")
```

With all model parameters kept constant as in the output shown in (fig \@ref(fig:abm3)), we can run the model with just 5% of the agents assigned as having the possibility to defect at initialization and all agents modifying harvest strategies via success-biased learning. The average final time step outcomes from five runs of this model can be seen in (fig \@ref(fig:abm4)).

```{r abm4, out.width = "75%",echo=FALSE, fig.cap="Average harvest values for all agents in the final time step (30) across five runs of the model. Outcomes are the result of many combinations of resource mobilities and protected area sizes. Model starting conditions include 100 individuals harvesting from a landscape of 10000 resources. The regeneration factor at each time step is 1.20 and the maximum harvest value is set to 25. Five percent of agents assigned to defect at initialization. Agents learn through success-biased learning.", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmp4.png")
```
Allowing agents to modify harvest strategies and harvest from the protected area greatly reduces the overall harvest outcomes. To better understand the underlying dynamics, we set the starting model parameters to the ideal conditions for maximum payoff as identified in (fig \@ref(fig:abm3)) and observe the model behavior at each time step.

```{r abm5, out.width = "100%",echo=FALSE, fig.cap="Five runs of the agent-based model. Thin black lines show each run. Thick black lines show the average values across runs. Starting conditions include 100 individuals harvesting from a landscape of 10000 resources. Eighty percent of resources are inside the protected area and the probability of resource mobility is 100 percent. The regeneration factor at each time step is 1.20 and the maximum harvest value is set to 25. Five percent of agents assigned to defect at initialization. Agents learn through success-biased learning.", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ABM_Output.png")
```

Model dynamics show that over time, agents begin to harvest from the protected area as they copy more successful individuals. This behavior depletes the resource pool in the protected area and lowers the number of resources which regenerate and agents can harvest in the subsequent time step. Note that full defection is defined as agents spending an equal proportion of their effort in the protected area as the proportion protected (i.e. they treat the entire landscape equally).

The results displayed above are for one homogenous group of agents harvesting resources from a common pool of resources. This model is useful for exploring the sink/source utility of protected areas to ensure long-term resource provisioning, especially in the contexts of social learning. To further explore this model, I have created an interactive application which performs one run of the model and can be found here [(click!)](https://mattclarknewaccount.shinyapps.io/ABM_Output_trial/). Comparing these model runs to simple analytical models and our intuition about how the model should behave also allows us to ensure that the model is functioning properly. To address the research question of interest however, we will need to update the model to include multiple interacting groups.

```{r tabAbmVars, echo=F, fig.align='center'}
abmVars <- data.frame(Parameters = c("Individuals","Total Carrying Capacity", "Percent Carrying Capacity", 
                                    "Percent Protected", "Starting Cooperators", "Time Steps", "Max Harvest",
                                     "Resource Regeneration",  "Resource Mobility","Groups","Learning Strategy", 
                                     "Percent Cooperation", "Average Payoff", "Protected Area Degradation",
                                     "Working Landscape Degradation"), 
                      Type = c("Starting Condition","Starting Condition","Starting Condition",
                               "Starting Condition","Starting Condition","Starting Condition",
                               "Starting Condition","Key Independent Variable","Key Independent Variable",
                               "Key Independent Variable","Key Independent Variable",
                               "Outcome","Outcome","Outcome","Outcome"), 
                      Description = linebreak(c("Number of agents in simulation",
                                      "Maximum number of resources allowed on landscape",
                                      "Percent of carrying capacity at initialization",
                                      "Percent of landscape in protected area",
                                      "Starting percent of agents fully cooperating",
                                      "Number of time steps simulation will run for",
                                      "Maximum number of resources agents will harvest during one time step",
                                      "The percent of available resources which will regenerate at each time step in both protected and working landscapes",
                                      "The probability that any available resource will move from the  protected to working landscape or vice versa",
                                      "Solitary or multiple competing groups",
                                      "Assigns a percent of the population to success-biased imitation and the remaining population to conformist-biased imitation",
                                      "Percent of total population harvest time spent in the working landscape","Mean harvest for all agents at each time step",
                                      "Working landscape percent of total carrying capacity",
                                      "Protected area percent of total carrying capacity")))
kbl(abmVars,format="latex", caption = "Description of all model variables and outcomes",escape=F) %>% 
  kable_classic_2(full_width=F)%>% row_spec(0,bold=TRUE)%>%
    column_spec(1, width = "8em")%>%
    column_spec(2, width = "8em")%>%
  column_spec(3, width = "20em")

@@

*Proposed Multi-Group Model*

In the multiple interacting groups scenario, two groups with separate resource pools will each follow the processes described above. However, at the end of each time step the groups will compare the average harvest rates. We assume that the underperforming group can observe the average harvest strategy (time spent in the protected or working areas) of the better performing group. A specified percent of the agents from the less successful group will subsequently adopt the average harvest strategy of the more successful group (see Table \@ref(tab:tabAbmVars)).

@@

## Expected Products
I plan to communicate the findings of this project both to the academic community and to non-scientists. The insights gained from this model will be published in a peer reviewed, academic journal such as Environmental Modeling and Software. This paper will show logically how we expect that protected areas function in the context of community level cooperative conservation. I also expect that this research will provide actionable insights for how designing protected areas while considering inter-group dynamics may allow for optimal resource provisioning under a much more broad set of circumstances than considering solitary groups alone.

@@

@@

In summary, conserving forest cover is critical for the global carbon balance and for the well-being of many rural communities. Conservation projects often fail due to a lack of consideration of the social processes underlying adoption. With few studies that measure transmission fidelity in a naturalistic setting, where outcomes have real economic and health impacts - we have an opportunity to explore how environmental constraints and social learning interact when outcomes matter. This project seeks to further investigate how and why behaviors are modified during the transmission process and how modification (both erroneous and intentional) affect performance targets.

@@

```{r mapp, echo=FALSE, fig.cap="Satellite map of Pemba Island, Tanzania. Three marked locations are the wards which will be surveyed for fuel-efficient cookstove copying fidelity and outcomes.", out.width = "75%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/InsetMap.png")
```
